---
title: "Moh R"
author: "Faizan Khalid Mohsin"
date: "September 11, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r }

require(readxl)

```



```{r }

data1 = read_excel("Data Part 1 for Faizan.xlsx")


```

## Part 1 
Check if TST and SO-TST columns are normally distributed (use shapiro-wilk test). 

```{r}
shapiro.test(data1[[2]])

shapiro.test(data1[[4]])


```


Make a t-test between them.


```{r}
t.test(data1[,2], data1[,4])
```


Check if SE and SO-SE coloumns are normally distributed (use visual method like density plot or qq plot)  


```{r}

qqnorm(data1[[3]], pch = 1, frame = FALSE)
qqline(data1[[3]], col = "steelblue", lwd = 2)


qqnorm(data1[[5]], pch = 1, frame = FALSE)
qqline(data1[[5]], col = "steelblue", lwd = 2)


```


Make a t test between them.


```{r}

t.test(data1[,3], data1[,5])
```


Part2  

How many RWA episodes are they having in their REM bouts (an RWA bout is counted when the value is greater or equal to 50), I just want the raw number value of how many there are per subject in each of the treatments 

```{r}

data2 = read_excel("Data Part 2 for Faizan.xlsx", sheet = 2)
data2so = read_excel("Data Part 2 for Faizan.xlsx", sheet = 3)

data2_count = data2[,2:6] > 50
count = rowSums(data2_count)

data2so_count = data2so[,2:6] > 50
countso = rowSums(data2so_count)

final_data = data.frame(Name = data2[[1]], RWA = count, RWA_SO = countso )

final_data

```










